%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.4in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------the candidate will be assigned to a project team in Singapore which is involved in one of the Meinhardt projects. Intern’s contribution to the project will be specified and evaluated by an assigned coordinator.


%----------------------------------------------------------------------------------------
\moveleft.200\hoffset\centerline{Cover Letter}
To whom it may concern,

With this letter I would like to express my interest in Meinhardt internship program in Singapore. As I'm studying in Nazarbayev University (Astana, Kazakhstan), our Career and Advising Center has contacted us with the information about your company's internship programs. Currently I am a third year Electrical and Electronic Engineering undergraduate student. I think that I gained some knowledge in the field of electrical and electronic engineering and found some interest in this field. 

Moreover, I have passed an internship at the Engineering Center of the Department of the Material and Technical Supply which is a part of administration of the President of the Republic of Kazakhstan which provides all the technical part for proper operation of the Parliament. During this internship I have learnt how to collaborate with other engineers and perform group projects. 

During my undergraduate studies I had several courses which main purpose was to teach us to perform the individual or group projects, such as Software Engineering and Programming for Engineers, where we have implemented several projects in C and Java programming languages. Moreover, I have passed Digital Integrated and Electronic circuit design, Electronic Engineering Design Principles, where we were working on group project on specific hardware design, simulating and soldering the physical circuit. In my opinion, my knowledge in mentioned fields makes my a suitable candidate for your internship position.

Additionally, currently I'm enrolled as Research Assistant (RA) of our department professor's project which is connected with radio frequency circuit design. This field is quite new for me, but I think that I can go through these challenges and succeed in my research. This validates that I'm not afraid of complex problems and ready to solve them.

This internship would provide the ideal path for my future career. I am expecting to improve my group working and research skills and learn how to apply them in the industry. Also, working in such big and popular company can be a great first step for my future.

I hope to hear from you soon.

Best regards, 

Olzhas Shaikenov

 
\end{document}